Check Coverage

### 2019-10-22 analysis/merge_data.Rmd
Return the correct object from FD calculation function.

  as_tibble(dbFD_joggle(trait_mat, species_mat, w.abun = FALSE))[,1:8] %>%
    cbind(years, .) %>%
    mutate(study_id = unlist(study), plot = unlist(plot_num)) %>%
    write_tsv(paste0(here::here("data"), "/fd_output/", "s", study, "_p", plot_num, "_fd.tsv"))

  setwd(here::here())
}

@@

Read data back in:
```{r}
files <-  dir(here::here("data", "fd_output"), "*.tsv")

fd_data <- files %>%
  paste0(here::here("data", "fd_output"), "/", .) %>%
  map_dfr(read_tsv)

fd <- biotime_traits %>%
  filter(!is.na(plot), !study_id %in% c(195, 360)) %>%
  anti_join(fd_data) %>%
  group_by(study_id, year, plot) %>%
  filter(n_distinct(id) > 4) %>%
  ungroup() %>%
  group_by(study_id, plot) %>%
  group_map(~get_fd_safe(.x, study = .y$study_id, plot = .y$plot))

#4610981
#7611121

>>>>

  fd_out <- as_tibble(dbFD_joggle(trait_mat, species_mat, w.abun = FALSE))[,1:8] %>%
    cbind(years, .) %>%
    mutate(study_id = unlist(study), plot = unlist(plot_num)) %>%
    write_tsv(paste0(here::here("data"), "/fd_output/", "s", study, "_p", plot_num, "_fd.tsv"))

  setwd(here::here())
  return(fd_out)
}

@@

Read data back in:
```{r}
# files <-  dir(here::here("data", "fd_output"), "*.tsv")
# 
# fd_data <- files %>%
#   paste0(here::here("data", "fd_output"), "/", .) %>%
#   map_dfr(read_tsv)
# 
# fd <- biotime_traits %>%
#   filter(!is.na(plot), !study_id %in% c(195, 360)) %>%
#   anti_join(fd_data) %>%
#   group_by(study_id, year, plot) %>%
#   filter(n_distinct(id) > 4) %>%
#   ungroup() %>%
#   group_by(study_id, plot) %>%
#   group_map(~get_fd_safe(.x, study = .y$study_id, plot = .y$plot))
# 
# #4610981
# #7611121
